Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors

### 2019-02-11 paper/ms.tex
Progress on results section of Carlyn's paper.

{\color{red} ARE THE BELOW NUMBERS CORRECT?}
The C-O and C-O-Ne models have the same central density
and temperature $7 \times 10^8$~K, respectively.
The C-O model had core composition of (\C{12} = 0.4, 
\Ne{20} = 0.03, \Ox{16} = 0.57) and envelope composition 
of (\C{12} = 0.5, \Ne{20} = 0.02, \Ox{16} = 0.48). 
The C-O-Ne model had core composition of (\C{12} = 0.X, 
\Ne{20} = 0.XX, \Ox{16} = 0.XX) and envelope composition 
of (\C{12} = 0.XX, \Ne{20} = 0.0X, \Ox{16} = 0.XX). 
\figref{fig:co_vs_cone_temp} show the density and temperature 
profiles of the C-O and C-O-Ne hybrid WD.

@@

A plot of the estimated \Ni{56} yield as a function of the final, burned mass
for all CO and Hybrid runs. The Hybrid model is shown in red, and the CO
model is shown in blue. As it is shown, the CO model has a higher final mass
then the Hybrid model.

The cumulative distribution of the \Ni{56} yield for the C/O and hybrid
simulations is presented in \ref{fig:cumdist}. 
The figure presents the estimated \Ni{56} yield as a function of the final burned 
mass. The results show that the C/O models have a higher burned mass than the
hybrid models for a given estimated mass of \Ni{56}. CHECK THIS.

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_yield_cum_dist.pdf}
\caption{\label{fig:cumdist}
A plot of the estimated \Ni{56} yield as a function of the final, burned mass
for all CO and Hybrid runs. The Hybrid models are shown in red, and the CO
models are shown in blue. As it is shown, the CO model has a higher final mass
then the Hybrid model. 
}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_vs_time_hybrid.png}
\caption{\label{fig:nithybrid}
Estimated \Ni{56} mass vs.\ time for ten hybrid model explosion simulations. 
Shown are realizations 21-30. 
}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_vs_time_CO.png}
\caption{\label{fig:nitco}
Estimated \Ni{56} mass vs.\ time for ten C/O model explosion simulations.
Shown are realizations 21-30. 
}
\end{figure}

The figures show that the final Estimated \Ni{56} for the CO model is
slightly larger then the Hybrid model. Therefore, the CO produces more
\Ni{56}. The Hybrid model has a larger range then the CO model. Also, on
average, the CO model reaches the DDT phase sooner then the Hybrid model.

>>>>

{\color{red} ARE THE BELOW NUMBERS CORRECT?}
The C-O and C-O-Ne models have the same central density
and temperature $7 \times 10^8$~K, respectively.
The C-O model had core composition of (\C{12} = 0.4, 
\Ne{20} = 0.03, \Ox{16} = 0.57) and envelope composition 
of (\C{12} = 0.5, \Ne{20} = 0.02, \Ox{16} = 0.48). 
The C-O-Ne model had core composition of (\C{12} = 0.X, 
\Ne{20} = 0.XX, \Ox{16} = 0.XX) and envelope composition 
of (\C{12} = 0.XX, \Ne{20} = 0.0X, \Ox{16} = 0.XX). 
The profiles of the two-dimensional models match those of
the one-dimensional models (shown in \figref{fig:init_conds})
up to very slight errors from the mapping process. {\color{red}
OMIT THIS LAST SENTENCE? DONT HAVE A FIGURE}

@@

We frame the presention of the results of the suites of simulations 
principally in terms of the yield of \Ni{56}, the source of 
the light curve of an event. \Ni{56} thus serves as a proxy
for the brightness of an explosion and comparison of the yields
is equivalent to comparing the brightness events. The
yields estimated from $Y_e$ and the NSE progress
variable, by assuming the composition in NSE is \Ni{56} plus equal
parts \Fe{54} and \Ni{58}, as described in
\citet{townetal2009,Meaketal09}.

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_yield_cum_dist.pdf}
\caption{\label{fig:cumdist}
The cumulative distribution of the \Ni{56} yield for explosions from
C-O and hybrid C-O-Ne models. The hybrid results are shown in red, and the CO
results are shown in blue. The curve for the hybrid models is shifted 
to the left, indicating that explosions from hybrid progenitors produce
less \Ni{56} than explosions from traditional C-O models. 
}
\end{figure}
The cumulative distribution of the \Ni{56} yield for explosions from
C-O and hybrid C-O-Ne models is presented in \ref{fig:cumdist}. 
The figure shows that the hybrid models consistenly have a higher
cumulative fraction at a given mass of \Ni{56}, which indicates
that the yields of \Ni{56} are consistenly lower in explosions 
from hybrid progenitors. {\color{red} CHECK/EXPAND THIS}

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_vs_time_hybrid.png}
\caption{\label{fig:nithybrid}
Estimated \Ni{56} mass vs.\ time for ten hybrid model explosion simulations. 
Shown are realizations 21-30. 
}
\end{figure}
\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_vs_time_CO.png}
\caption{\label{fig:nitco}
Estimated \Ni{56} mass vs.\ time for ten C/O model explosion simulations.
Shown are realizations 21-30. 
}
\end{figure}
The estimated production of \Ni{56} as a function of simulation time
for 10 simulations of explosions from the hybrid progenitor is shown
in Figure \ref{fig:nithybrid} and from the traditional C-O progenitor is
shown in Figure \ref{fig:nitco}.
The figures show that the final Estimated \Ni{56} for the C-O model is
slightly larger then the hybrid model. Therefore, the C-O produces more
\Ni{56}. The hybrid model has a larger range then the C-O model. Also, on
average, the CO model reaches the DDT phase sooner then the hybrid model.
